---
title: 'BRM1_IBA_2021: Week 5'
<<<<<<< HEAD
author: "Fill in all student names and team number"
date: "11/3/2020"
=======
author: "Demi Maric,  Ashley Verdies, Merle, Team 117"
date: "5/3/2021"
>>>>>>> a8579ec1aabb3f202c5a49b585e73eab4263a2db
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Before you start, install your working environment 
- check your working directory
- setwd() to change working directory
- remove all objects, start with an empty environment

```{r}
getwd()
rm(list=ls()) 
<<<<<<< HEAD
setwd("~/github/BRM117")
=======
>>>>>>> a8579ec1aabb3f202c5a49b585e73eab4263a2db
```

Use same dataset as last week:
```{r}
# write your R code here
df<-read.csv("Netherlands_USA.csv", sep=",")
<<<<<<< HEAD
str(df)
=======
>>>>>>> a8579ec1aabb3f202c5a49b585e73eab4263a2db
```

# Assignment week 5 
Make sure that the estimates will be correct and include both with and without missings when making the R-rated movie dummy (see week 4).

# 1. Multiple regression per country
Estimate a regression model per country using imdb-rating and the R-rated movie dummy as independent variables to explain log transformed opening revenues. Report the unstandardized beta coefficient of imdb-rating and the R-rated movie dummy for country 1.
```{r}
# write your R code here
<<<<<<< HEAD
=======
df$MPAA_rating[df$MPAA_rating==" "]<-NA
df[df$MPAA_rating=="R" & !is.na(df$MPAA_rating),"R_rated"] <- 1
df[df$MPAA_rating!="R" & !is.na(df$MPAA_rating),"R_rated"] <- 0

lm(log(Opening_revenues)~imdb.com_rating + R_rated, data = df[df$Country=="USA",])


>>>>>>> a8579ec1aabb3f202c5a49b585e73eab4263a2db
```

# 2. Moderated regression
Estimate the same regression model as in 1) on the whole sample, but with country as moderator for the effect of imdb-rating and the R-rated movie dummy on the log transformed opening revenues. You need to add two moderators to the model using * (as shown in lecture). Report the unstandardized beta coefficient of imdb-rating and the R-rated movie dummy and the interaction effects.
```{r}
# write your R code here
<<<<<<< HEAD
=======

df$MPAA_rating[df$MPAA_rating == " "] <- NA
df$dummy[df$MPAA_rating == "R"] <- 1
df$dummy[df$MPAA_rating != "R" & !is.na(df$MPAA_rating)] <- 0

lm3<- lm(log(df$Opening_revenues) ~ df$Country*df$imdb.com_rating + df$dummy*df$Country, df)
summary(lm3)
>>>>>>> a8579ec1aabb3f202c5a49b585e73eab4263a2db
```

# 3. Prediction
Predict log revenue for an R-rated movie with a imdb-rating of 6.6 per country using the estimates from 2). Keep in mind country is treated as a dummy variable.
```{r}
# write your R code here
<<<<<<< HEAD
=======
##country 1
lm3$coeff[1]+lm3$coeff[2]*0+lm3$coeff[3]*6.6+lm3$coeff[4]*1+lm3$coeff[5]*0*6.6 + lm3$coeff[6]*0*1

## country 2
lm3$coeff[1]+lm3$coeff[2]*1+lm3$coeff[3]*6.6+lm3$coeff[4]*1+lm3$coeff[5]*1*6.6 + lm3$coeff[6]*1*1

>>>>>>> a8579ec1aabb3f202c5a49b585e73eab4263a2db
```

# 4. Mean centering
Mean-center the non-dummy variables included in the regression analysis (not the dependent variable!) and re-estimate the model estimated in step 2 on the whole sample. *Note*. Mean centering is across whole sample, not country-specific. Report the unstandardized coefficients for country 1. Use `relevel` and `factor` commands.
```{r}
# write your R code here
```

# 5. Interpretation
How would you interpret the intercept of model you've estimated under 4?

# 6. Prediction original scale
What is the predicted value of the opening revenues for an R-rated movie with an average imdb-rating? Use the coefficients of the model you've estimated in step 4. Report the predicted value of opening revenues at the **original scale** per country. 
```{r}
# write your R code here
```

