---
title: "BRM1_IBA_2021: Week 2"
author: "Fill in all student names and team number"
date: "11/3/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## before you start, install your working environment 
- check your working directory
- setwd() to change working directory, ?setwd to learn more
- start with an empty environment to prevent mistakes: 
  + remove all objects from the environment
  + read in the raw data file 


```{r}
getwd()
rm(list=ls()) # remove all objects
```

# Assignment week 2 

Continue with the data file of week 1
```{r}
# read in data file
# you can copy the code of last week
```

## 1. $t$-test
Test whether financial satisfaction `Q50` is lower than 6, and 
report the $t$-value and $p$-value. 
```{r}
# write your code here
```
How would you label this variable measuring satisfaction? **Likert, semantic difference scale, paired comparison, rank order, continuous rating scale, or Stapel.** 

## 2. Chisquare $X^2$ test
Analyze dependency between emancipation `Q31` and education recoded `Q276R`. Report the $X^2$ (=chisquare value), the p-value and interpret whether they are dependent or not.
```{r}
# write your code here
```
How would you label this variable measuring emancipation? **Likert, semantic difference scale, paired comparison, rank order, continuous rating scale, or Stapel.** 

## 3. Validity
Explore all seven items that measure female emancipation (`Q28`,`Q29`,`Q30`,`Q31`, `Q32`, `Q33`, and `Q35`) per country. Use pairwise deletion. Inspect the correlation matrix, and argue whether or not there is a high convergent validity for each country. 

*Note*: Country 1 is the country that comes first alphabetically.
```{r}
# write your code here
```
Does each correlation depend on the same observations?

## 4. Reliability

### Recoding
Recode the seven emancipation items so that a high number reflects a positive attitude towards female emancipation. Use indexing and what you've learned in the last assignment. Do NOT use `recode` from library `car`! Attach the recoded variables to your data with the addition `R` to their original variable names. Try to use a `for` [loop](https://www.tutorialspoint.com/r/r_for_loop.htm), and mind the `NA`s. Do not use listwise deletion! Check your results with cross tabulation.
```{r}
# write your code here
```

### Cronbach's Alpha
There are multiple formulas to calculate the Cronbach's alpha. One is defined as follows:
$$ alpha = \frac{k}{k-1} \left(1-\frac{\sum_{i}^k\sigma^2_{y_{i}}}{\sigma^2_{x}}\right)$$

where $k$ is the number of items, $\sigma^2_{x}$ is the variance of the observed total test scores, and $\sigma^2_{y_{i}}$ is the variance of the $i$th item. 

```{r}
# first calculate number of items and save to object k


# then calculate the variance for all items per item using var()
# to make it easier, we use listwise deletion (use="complete.obs")
# use diag() to get to the variances
# sum the variances using sum()


# lastly, calculate the variance of total test score
# which is the sum of all covariances and variances

# fill in formula
```

The Spearman-Brown Prophecy Formula is easier to calculate, and referred to as the standardized Cronbach's alpha. The standardized Cronbach's alpha is defined as follows:

$$alpha_{st} = \frac{k * \overline{r}}{1+(k-1) * \overline{r}}$$

Calculate the standardized Cronbach's alpha in the same way as is done with the Cronbach's alpha above but now use the correlation matrix (see point 3) instead of the variance-covariance matrix. It helps if you save the correlation matrix in an R object, and then retrieve the correlations with `lower.tri` using indexing. Do this separately per country, and use pairwise deletion. 

```{r}
# write your code here
```

You can check whether you did it correctly, using the `psych` package. Install the package first. I also had to download [Rtools](https://cran.rstudio.com/bin/windows/Rtools/). Select the .exe file suitable for your operating system. Make sure you do this separately for each country!

```{r}
# check with alpha() from psych package 
# install.packages("psych")
library(psych)
# write your code here
```

## 5. Calculate mean scores
Calculate for each person in your data a mean score across the seven items mentioned above. Use `apply`, mind the missings. Attach this variable as a new variable labeled `emanci` to your data file. Report the absolute mean differences between these countries in `emanci` using `abs`.
```{r}
# write your code here
```

## 6. Scatter plot
Plot the relationship of satisfaction financial situation (x-axis) and emancipation (y-axis). Make sure you use the mean scores calculated under 5). Create the plot separately for each country. 
```{r}
# write your code here
```

## 7. Create age dummy
Create a dummy variable equal to 1 if millennial (age 15 – 34) and 0 otherwise. To clarify: people aged 34 are labeled 1, and people aged 35 are labeled 0. Use the age variable `Q262`. Make sure missing cases in the original variable are also missing in the dummy variable. What percentage of the population is millennial in country 1?
```{r}
# write your code here
```

Inspect the average value and standard deviation of emancipation item `Q31` per this dummy variable. Use `tapply`. Is the mean difference significantly different from zero (using a 95% confidence interval)? Use `t.test` on the whole dataset including both countries. *Note*: make sure the decimal is recognized as such by Excel (check worksheet named `OUTPUT`)
```{r}
# write your code here
```

